\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cite}

\geometry{margin=1in}
\title{Progress Report: Investigating the Impact of Higher-Degree NLFSR Feedback Functions on Cryptographic Strength and Periodicity}
\author{
    Abdulmumin Sa'ad \\
    Mohammed Mansour \\
    Supervised by: Prof. S. Almuhammadi \\
    King Fahd University of Petroleum and Minerals (KFUPM)
}
\date{\today}

\begin{document}

\maketitle

\section*{Executive Summary}
This progress report outlines the current status of the project titled \textit{Investigating the Impact of Higher-Degree NLFSR Feedback Functions on Cryptographic Strength and Periodicity}. The objective is to explore feedback functions of NLFSRs with algebraic degrees higher than three and assess their potential cryptographic benefits. To date, preliminary construction and analysis have been performed, with a focus on understanding period behavior and resistance to known cryptanalytic attacks.

\section{Progress Overview}
\subsection{Completed Work}
\begin{itemize}
    \item Conducted literature review on existing NLFSR constructions, particularly those of degrees 2 and 3.
    \item Developed initial models for higher-degree feedback functions (degree 4).
    \item Implemented test NLFSR sequences and measured period lengths.
    \item Conducted preliminary evaluation of resistance to correlation attacks.
\end{itemize}

\subsection{Ongoing Work}
\begin{itemize}
    \item Extending experimental framework to higher degrees and larger state sizes.
    \item Refining algebraic analysis tools for cryptographic strength evaluation.
    \item Comparing new constructions with known optimal NLFSRs from literature.
\end{itemize}

\subsection{Issues Encountered}
\begin{itemize}
    \item Increased complexity of higher-degree functions has led to longer computation times.
    \item Difficulty in obtaining benchmark results for comparison with optimal known constructions.
\end{itemize}

\section{Revised Timeline}
\begin{itemize}
    \item \textbf{Month 1-2:} Literature review and theoretical exploration (Completed)
    \item \textbf{Month 3-4:} Implementation of initial models and testing (Completed)
    \item \textbf{Month 5-6:} Extended analysis and comparison (Ongoing)
    \item \textbf{Month 7:} Final evaluation and report writing (Upcoming)
\end{itemize}

\section{Next Steps}
\begin{itemize}
    \item Finalize experimental framework for degree 4.
    \item Evaluate cryptographic metrics such as nonlinearity and algebraic immunity.
    \item Prepare final results and draft the concluding research paper.
\end{itemize}

\end{document}
